### 2015-06-11 testing-code/check-sim.Rmd
.

# Simulated parameter values
```{r, echo=FALSE, results="asis"}
params <- as.data.frame( matrix( c(
        time,
        simseq.config$tip$mutrates,
        simseq.config$tip$selcoef,
        simseq.config$tip$fixfn.params
    ), nrow=1 ) )
colnames(params) <- gsub("|","\\|",c(
        "time",
        mutnames(simseq.config$tip$mutpats),
        selnames(simseq.config$tip$selpats),
        names(simseq.config$tip$fixfn.params)
    ), fixed=TRUE)
pandoc.table(params, style="rmarkdown")
```

>>>>

# Simulated parameter values
```{r, echo=FALSE, results="asis"}
params <- as.data.frame( matrix( c(
        time,
        simseq.config$tip$mutrates,
        simseq.config$tip$selcoef,
        simseq.config$tip$fixfn.params
    ), nrow=1 ) )
colnames(params) <- gsub("|","\\|",c(
        "time",
        mutnames(simseq.config$tip$mutpats,pretty=TRUE),
        selnames(simseq.config$tip$selpats,pretty=TRUE),
        names(simseq.config$tip$fixfn.params)
    ), fixed=TRUE)
pandoc.table(params, style="rmarkdown")
```
